### 2023-11-28 manuscript.tex
Updated hierarchy caption to reflect log-likelihood and removal of cluster descriptions

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy.png}
\centering
\caption{\textbf{Hierarchical clustering of evolutionary signatures.}
The AIC difference between the BM and OU models is measure of their relative goodness of fit to the data with a penalty for the number of parameters in each. Larger values indicate a better fit by the OU model. Clusters are indicated by rectangles on the right. The cluster descriptions are summaries of selected significantly enriched annotations ($p < 0.01$) and do not necessarily correspond to specific terms.}
\label{fig:hierarchy}
\end{figure}

>>>>

\begin{figure}[h!]
\includegraphics[width=\textwidth]{hierarchy/out/hierarchy.png}
\centering
\caption{\textbf{Hierarchical clustering of evolutionary signatures.}
The log likelihood ratio between the BM and OU models is measure of their relative goodness of fit to the data. Larger values indicate a better fit by the OU model. Clusters are indicated by rectangles on the right. Clusters with fewer than 75 regions are omitted for clarity.}
\label{fig:hierarchy}
\end{figure}
